Verifying Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-04-27 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed introduction
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. 
Progress has been made worldwide; in particular, the number of people without electricity access 
fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}. 
In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) 
in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed; 
specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.

In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., 
RETScreen, and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 However, those tools are based on simulations; they have the drawback of an incomplete coverage 
 since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.

Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of systems~\cite{ClarkeHV18}. %Therefore, in the context of this proposal, a CPS, specifically a PV system, is the target. We review verification tools and related them to design and to PV systems verification, which was uncommon in prior studies~\cite{abs-1811-09438}.

\textcolor{red}{There is no connection between both paragraphs.}

>>>>

Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. 
Progress has been made worldwide; in particular, the number of people without electricity access 
fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}. 
In order to provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) 
in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed \textcolor{red}{Add reference here}; 
specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.

In order to simulate or evaluate a PV system, there exist various specialized tools available in the market, e.g., 
RETScreen, and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 However, those tools are based on simulation; they have the drawback of an incomplete coverage 
 since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.
Formal methods based on \textit{model checking} can offer a great potential to obtain a more effective design process of CPSs~\cite{ClarkeHV18}. %Therefore, in the context of this proposal, a CPS, specifically a PV system, is the target. We review verification tools and related them to design and to PV systems verification, which was uncommon in prior studies~\cite{abs-1811-09438}.

\textcolor{red}{We should rewrite the following paragraph as follows.}

\textcolor{red}{In summary, this paper makes the following original contributions.
\begin{itemize}
\item First contribution.
\item Second contribution.
\end{itemize}
}

\textcolor{red}{Address a CPS is not a contribution...}
